Chr2 hotspot analyses

### 2019-07-15 analysis/paper/Chr2-hclusterings.Rmd
updated Chr2 analyses.

```{r all-pleio}
foo %>%
  dplyr::select(9, 10, 3, 8, 1, 2) %>%
  rename(gene1_id = nonlocal_gene_id,
         gene2_id = local_gene_id,
         gene1_symbol = nonlocal_symbol, 
         gene2_symbol = local_symbol
         ) %>%
  bind_rows(local_pleio) %>%
  bind_rows(nonlocal_pleio) %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

>>>>

```{r all-pleio}
foohc <- foo %>%
  dplyr::select(9, 10, 3, 8, 1, 2) %>%
  rename(gene1_id = nonlocal_gene_id,
         gene2_id = local_gene_id,
         gene1_symbol = nonlocal_symbol, 
         gene2_symbol = local_symbol
         ) %>%
  bind_rows(local_pleio) %>%
  bind_rows(nonlocal_pleio) %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  (function(x) {
    hc <- dist(x) %>% hclust()
    return(x[hc$order, hc$order])
    }
   ) %>%
  (function(x) {
    cols <- c("green", "orange")[1 + (colnames(x) %in% bar$nonlocal_symbol)]
    heatmap.2(x, symm = TRUE, dendrogram = "both", na.rm = TRUE, ColSideColors = cols, cexRow = 0.2, cexCol = 0.2)
              }
   )
```
